A Formal Model of Checked C

### 2023-01-08 sandp23/introduction.tex
[review] comments/revision on the first paragraph

Vulnerabilities due to memory corruption, especially spatial memory corruption, 
are still a major issue for C programs~\cite{cvetrend, microsoftmemsafe, Zeng:2013:SRF:2534766.2534798} 
despite a large body of work that tries to prevent them~\cite{song2019sanitizing}.
Several industrial and research efforts, including CCured~\cite{Necula2005},
Softbound~\cite{softbound}, and ASAN~\cite{Serebryany2012},
have investigated ways to compile C programs 
to automatic spatial safety enforcement.
These approaches all impose performance overheads deemed too high for deployment use. 
\liyi{Should we say this? Is the paper about overhead reducing? }
Recently,~\citet{Elliott2018} and~\citet{li22checkedc} introduced and formalized \checkedc, an
open-source extension to C with new types and
annotations to ensure a program’s spatial safety.
Specifically, \checkedc extends C with checked pointer types, which are restricted by the compiler to spatially safe uses.
The checked pointers are represented as system-level memory words,~\ie without ``fattening'' metadata, ensuring backward compatibility.
This enables incremental conversion, where regions of code can be converted to~\checkedc and ensure spatial safety within those regions.
However, as we explain in~\sect{subsec:nosafetyagsintuncheckedcode}, the unconverted or unchecked code can violate guarantees provided in Checked regions.
%
We need to ensure that~\emph{code executed as part of unchecked regions does not violate the safety guarantees in checked regions}.

>>>>

Vulnerabilities due to memory corruption, especially spatial memory corruption, 
are still a major issue for C programs~\cite{cvetrend, microsoftmemsafe, Zeng:2013:SRF:2534766.2534798} 
despite a large body of work that tries to prevent them~\cite{song2019sanitizing}.
Several industrial and research efforts, including CCured~\cite{Necula2005},
Softbound~\cite{softbound}, and ASAN~\cite{Serebryany2012},
have investigated ways to
\mzu{compile C programs 
  to automatic spatial safety enforcement.}
\mz{You cannot compile a program to enforcement.}
% 
These approaches all impose performance overheads deemed too high for deployment use. 
% 
\liyi{Should we say this? Is the paper about overhead reducing? }
Recently,~\citet{Elliott2018} and~\citet{li22checkedc} introduced and formalized \checkedc, an
open-source extension to C
% 
\mzs{ with new types and annotations to ensure a program’s spatial safety.
  Specifically, \checkedc extends C with checked pointer types, which are
  restricted by the compiler to spatially safe uses.}
% 
\mzr{ with additional annotations and types, checked pointer types in
  particular, to ensure a program’s spatial safety.}
% 
\mz{Redundancy?}
% 
The checked pointers are represented as system-level memory words\mzs{,~\ie} without ``fattening'' metadata, ensuring backward compatibility.
\mz{\ie{} sounds indirect and redundant to me.}
% 
\mzu{This enables incremental conversion, where regions of code can be converted to~\checkedc and ensure spatial safety within those regions.}
\mz{This sentence is incoherent. I don't understand the connection between
  incremental conversion and regions of code. 
  % 
  I guess your point is that since you don't introduce extra metadata, 
  checked and unchecked region can coexist and interact seamlessly.
  % 
}
% 
However, as we explain in~\sect{subsec:nosafetyagsintuncheckedcode}, the
unconverted or unchecked code can violate guarantees provided in \mzu{Checked}
\mz{either tt it or use lowercase?}
regions.
%
We need to ensure that~\emph{code executed as part of unchecked regions does not violate the safety guarantees in checked regions}.
